Hierarchical Controller Architecture in Software Defined Networks

### 2013-12-16 paper/paper.tex
authors
mini minor change

\title{Hierarchical Controller Architecture in Software Defined Networks}
\author{
        Author 1 \\
            \and
        Author 2\\
        %UIUC\\
			\and
		Author 3\\
}
\date{\today}

\documentclass[10pt, twocolumn]{article}
\usepackage{url,graphicx,tabularx,array,geometry, caption, subcaption, float}
%-- Commands for header
\renewcommand{\title}[1]{\textbf{#1}\\}
\renewcommand{\line}{\begin{tabularx}{\textwidth}{X>{\raggedleft}X}\hline\\\end{tabularx}\\[-0.10cm]}
\newcommand{\leftright}[2]{\begin{tabularx}{\textwidth}{X>{\raggedleft}X}#1%
& #2\\\end{tabularx}\\[-0.10cm]}

@@

\subsection{Optimization}
Let's say there are \emph{n} controller domains. Each controller domain, $i$ maintains a vector timestamp $T_{i}[1...n]$, where $T_{i}[j]$ contains the latest revision number of domain $j$'s network state (link utilizations), seen by domain $i$. Whenever links utilization is revised for links in domain $i$, the controller increments its own revision number $T_{i}[i]$ in the timestamp. Timestamps are sent along with the network state to other controllers for replication. During replication, a controller revises its timestamp with the incoming timestamp by taking maximum for each entry between the two timestamps. This is a general technique for any replicated system. Each router is updated with the latest timestamp of its parent controller.

>>>>

\title{Hierarchical Controller Architecture in Software Defined Networks}
\author{
        Gourav Khaneja \\
	UIUC \\
	khaneja2@illinois.edu \\
            \and
        Sweta Seethamraju\\
        UIUC\\
	seetham2@illinois.edu \\
			\and
	Praveen Kumar\\
	IBM \\
	praveek7@in.ibm.com \\
}

\date{}
\documentclass[10pt, twocolumn]{article}
\usepackage{url,graphicx,tabularx,array,geometry, caption, subcaption, float}
%-- Commands for header
\renewcommand{\title}[1]{\textbf{#1}\\}
\renewcommand{\line}{\begin{tabularx}{\textwidth}{X>{\raggedleft}X}\hline\\\end{tabularx}\\[-0.10cm]}
\newcommand{\leftright}[2]{\begin{tabularx}{\textwidth}{X>{\raggedleft}X}#1%
& #2\\\end{tabularx}\\[-0.10cm]}

@@

\subsection{Optimization}
Let's say there are \emph{n} controller domains. Each controller domain, $i$ maintains a vector timestamp $T_{i}[1...n]$, where $T_{i}[j]$ contains the latest revision number of domain $j$'s network state (link utilizations), seen by domain $i$. Whenever link utilizations are revised for links in domain $i$, the controller increments its own revision number $T_{i}[i]$ in the timestamp. Timestamps are sent along with the network state to other controllers for replication. During replication, a controller revises its timestamp with the incoming timestamp by taking maximum for each entry between the two timestamps. This is a general technique for any replicated system. Each router is updated with the latest timestamp of its parent controller.
